---
title: "Scoring_questionnaires2021"
author: "Helio"
date: "21/08/2021"
output: html_document
---

gorilla codes


STAI:: 5nzr
AQ:7uqw
STAIS: 8rfo
Demog: 8zto
BVAQ: 83b1
BPQ: bbc4
DASS: chif
IQ: esh8
IAS: jvi8
TAS:pdlt
demog_meantal health: v2gn

AQ_50

quick check that Lucys scoring are correct

```{r}
# Traditional scoring

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")

library(readr)

db_quest_checkAQ<- read_csv("data_exp_11458-v8_questionnaire-7uqw.csv")
View(db_quest_checkAQ)

library(tidyverse)
colnames(db_quest_checkAQ)

db_quest_checkAQ<- db_quest_checkAQ%>%
  select(c(16,31:130))
  
db_quest_checkAQ_1<- db_quest_checkAQ%>%
select(seq(1, 101, 2))



# create a prefix for AQ items
# https://it.unt.edu/sites/default/files/paste_jds_jun2013.pdf - some nice tips here
prefix<- "AQ_"

AQ_counter<- seq(1,50)


aq_labels<-paste(prefix, AQ_counter, sep = "")
# generate odd numbers to match the columns we wnt to keep
names<- c("completion_code", aq_labels)

# rename dataset
names(db_quest_checkAQ_1)<- names

db_quest_checkAQ_2<- db_quest_checkAQ_1 %>%
#   mutate_at(c('TAS_4', 'TAS_5', 'TAS_10', 'TAS_18', 'TAS_19'), 
#             funs(recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
# #    2, 4, 5, 6, 7, 9, 12, 13, 16, 18,
# # 19, 20, 21, 22, 23, 26, 33, 35, 39, 41, 42, 43, 45, 46
  mutate_at(c("AQ_2", "AQ_4", "AQ_5", "AQ_6", "AQ_7", "AQ_9", "AQ_12", "AQ_13", "AQ_16", "AQ_18",
                 "AQ_19","AQ_20", "AQ_21", "AQ_22", "AQ_23", "AQ_26", "AQ_33", "AQ_35", "AQ_39", "AQ_41",
                 "AQ_42",
                 "AQ_43", "AQ_45", "AQ_46"), 
            funs(ifelse(. <= 2, 1, 0)))%>%
            # funs(recode(., "1=1; 2=1; 3=0; 4=0")))%>%
   mutate_at(c("AQ_1", "AQ_3", "AQ_8", "AQ_10", "AQ_11", "AQ_14", "AQ_15", "AQ_17", "AQ_24", "AQ_25",
                 "AQ_27","AQ_28", "AQ_29", "AQ_30", "AQ_31", "AQ_32", "AQ_34", "AQ_36", "AQ_37", "AQ_38",
                 "AQ_40",
                 "AQ_44", "AQ_47", "AQ_48", "AQ_49", "AQ_50"), 
             funs(ifelse(. > 2, 1, 0)))
             # funs(recode(., "1=0; 2=0; 3=1; 4=1")))



db_quest_checkAQ_2%>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ_Total = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ_Total))
  ggplot(aes(TAS_Total, AQ_Total))+
  geom_point()+
  facet_grid(~Dataset)
  
```

this confirms that Lucy scoring is correct
also checked a few examples of TAS seem correct. but should note one inconsistency in the first participant (300)

AQ_50

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/AQ")
# 345_356
read_selfrep1 <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}


# lvevkz = 356
db_aq_356<- subset(db_AQ, `Participant Completion Code` == "lvevkz")

db_AQ_backup<- db_AQ

db_AQ <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep1(.))

# db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")


unique(db_AQ$`Participant Completion Code`)
unique(db_AQ$`Participant Public ID`)

db_AQ<- subset(db_AQ, db_AQ$`Event Index`== 1)
  
  
View(db_AQ)

library(tidyverse)
colnames(db_AQ)
colnames(db_aq_356)

db_AQ<- bind_rows(db_AQ, db_aq_356)


colnames(db_AQ)

db_AQ$completion_code<- db_AQ$`Participant Completion Code`

db_AQ1<- db_AQ%>%
  select(c(18,34:133))
  

colnames(db_AQ1)

# selecting quqntised
db_AQ2<- db_AQ1%>%
select(seq(1, 101, 2))

colnames(db_AQ2)

# create a prefix for AQ items
# https://it.unt.edu/sites/default/files/paste_jds_jun2013.pdf - some nice tips here
prefix<- "AQ_"

AQ_counter<- seq(1,50)

aq_labels<-paste(prefix, AQ_counter, sep = "")

# generate odd numbers to match the columns we wnt to keep
names<- c("completion_code", aq_labels)

# rename dataset
names(db_AQ2)<- names

db_AQ3<- db_AQ2 %>%
#   mutate_at(c('TAS_4', 'TAS_5', 'TAS_10', 'TAS_18', 'TAS_19'), 
#             funs(recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
# #    2, 4, 5, 6, 7, 9, 12, 13, 16, 18,
# # 19, 20, 21, 22, 23, 26, 33, 35, 39, 41, 42, 43, 45, 46
  mutate_at(c("AQ_2", "AQ_4", "AQ_5", "AQ_6", "AQ_7", "AQ_9", "AQ_12", "AQ_13", "AQ_16", "AQ_18",
                 "AQ_19","AQ_20", "AQ_21", "AQ_22", "AQ_23", "AQ_26", "AQ_33", "AQ_35", "AQ_39", "AQ_41",
                 "AQ_42",
                 "AQ_43", "AQ_45", "AQ_46"), 
            funs(ifelse(. <= 2, 1, 0)))%>%
            # funs(recode(., "1=1; 2=1; 3=0; 4=0")))%>%
   mutate_at(c("AQ_1", "AQ_3", "AQ_8", "AQ_10", "AQ_11", "AQ_14", "AQ_15", "AQ_17", "AQ_24", "AQ_25",
                 "AQ_27","AQ_28", "AQ_29", "AQ_30", "AQ_31", "AQ_32", "AQ_34", "AQ_36", "AQ_37", "AQ_38",
                 "AQ_40",
                 "AQ_44", "AQ_47", "AQ_48", "AQ_49", "AQ_50"), 
             funs(ifelse(. > 2, 1, 0)))
             # funs(recode(., "1=0; 2=0; 3=1; 4=1")))



db_AQ4<- db_AQ3 %>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ))
  

db_AQ4

```

TAS-28

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/356_557_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_TAS <- list.files(pattern = "*-pdlt.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_TAS_backup<- db_TAS
db_TAS_356<- subset(db_TAS, `Participant Completion Code` == "lvevkz")


db_TAS <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))


library(readxl)
# db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")

db_TAS<- subset(db_TAS, db_TAS$`Event Index`== 1)
  
  
# View(db_TAS)

library(tidyverse)
colnames(db_TAS)
colnames(db_TAS_356)
db_TAS<- bind_rows(db_TAS, db_TAS_356)

db_TAS1<- db_TAS%>%
  select(c(16,32:71))
  

colnames(db_TAS1)

db_TAS2<- db_TAS1%>%
select(c(1,seq(2, 40, 2)))


colnames(db_TAS2)
# note the gorilal tas labels have a zero, like 01 instead of 1
?recode

db_TAS3<- db_TAS2 %>%
  mutate_at(c('TAS_04', 'TAS_05', 'TAS_10', 'TAS_18', 'TAS_19'), 
            funs(car::recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
  mutate(DIF = TAS_01 + TAS_03 + TAS_06 + TAS_07 + TAS_09 + TAS_13+ TAS_14)%>%
  mutate(EOT = TAS_08+TAS_15+TAS_16+TAS_20+TAS_05+TAS_10+TAS_18+TAS_19)%>%
  mutate(DDF = TAS_02+TAS_11+TAS_12+TAS_17+TAS_04)%>%
  mutate(TAS = DIF + DDF + EOT)

db_TAS3$completion_code<- db_TAS3$`Participant Completion Code`

db_TAS4<- select(db_TAS3, c(completion_code, TAS))
  


```

DASS: chif

# Function that scores DASS-21 and all subscales. DASS-21 is a 21-item scale
# (0-3 likert) measuring the participant's levels of depression, anxiety, and 
# stress. DASS is based on a dimensional understanding of these factors - 
# each of the 21 items is mapped to one of the three factors.
# Dependencies: tidyverse, 03_scoring_helpers.R

subscales need to be multiplied by 2

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/356_357_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_DASS_backup<- db_DASS
unique(db_DASS$`Participant Completion Code`)
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

db_DASS <- list.files(pattern = "*-chif.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

library(readr)

# db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
# 
# ("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")

db_DASS<- subset(db_DASS, db_DASS$`Event Index`== 1)


db_DASS<-  bind_rows(db_DASS, db_DASS_356)

colnames(db_DASS)

db_DASS1<- db_DASS%>%
  select(c(14,15,18,34:74))
  

colnames(db_DASS1)
db_DASS1$`Repeat Key`<- NULL

db_DASS1$completi

db_DASS2<- db_DASS1%>%
select(c(1:3,seq(4, 44, 2)))
colnames(db_DASS2)

db_DASS2$DASS_08<- db_DASS2$STAI_08
  
db_DASS2$STAI_08<- NULL

db_DASS3 <- db_DASS2 %>%
  # mutate(DASS_score_total =         rowsum(
  #                                      DASS_01:DASS_21))
  #   
    # Depression subscale is items 3, 5, 10, 13, 16, 17, and 21
    mutate(DASSDepression = 2*(DASS_03+ DASS_05+ DASS_10+ DASS_13+
                                       DASS_16+ DASS_17+ DASS_21),
    # Anxiety subscale is items 2, 4, 7, 9, 15, 19, and 20
    DASSAnxiety =    2*(DASS_02+ DASS_04+ DASS_07+ DASS_09+
                                       DASS_15+ DASS_19+ DASS_20),
    
    # Stress subsccale is items 1, 6, 8, 11, 12, 14, and 18
    # on gorilla DAS_08 is islabeled STAI_08
    DASSStress =     2*(DASS_01+ DASS_06+ DASS_08+ DASS_11+
                                       DASS_12+ DASS_14+ DASS_18)
    )%>%
  mutate(DASSTotal = DASSDepression+DASSAnxiety+DASSStress)
  
colnames(db_DASS3)
db_DASS3$completion_code<- db_DASS3$`Participant Completion Code`

db_DASS4<- select(db_DASS3, c(1:2,29,25:29))
db_DASS4

```

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/


hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r eval=FALSE, include=FALSE}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)

library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/All_scores_IAS350_2021-08-23.csv")
db_IAS

db_TAS_backup$`Participant Private ID`[db_TAS_backup$`Participant Completion Code` == "lvevkz"]

db_IAS_356<- subset(db_IAS, db_IAS$`Participant Private ID` == 4520106)
db_IAS_backup<- db_IAS

# library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/356_357_611_616/356_357_611_616All_scores_ias_2021-09-13.csv")
View(db_IAS)
```



BPQ: bbc4

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r}
# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/356_357_611_616")

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}
library(readxl)
# db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
# View(data_exp_11458_v9_questionnaire_bbc4)


library(readxl)
# db_BPQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/data_exp_11458-v9_questionnaire-bbc4-4489770.xlsx")

db_BPQ_backup<- db_BPQ
db_BPQ_356<- subset(db_BPQ, db_BPQ$completion_code == "lvevkz")

db_BPQ <- list.files(pattern = "*-bbc4.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

# eliminate empty rows
db_BPQ<- subset(db_BPQ, db_BPQ$`Event Index`== 1)

db_BPQ$completion_code<- db_BPQ$`Participant Completion Code`

db_BPQ_356$`Event Index`<- as.character(db_BPQ_356$`Event Index`)
db_BPQ<- bind_rows(db_BPQ, db_BPQ_356)

# store names for BPQ columns
bpq_names<- names(db_BPQ %>%
  
# score_BPQ <- function(df){
  # Create a new temporary df to store the BPQ data 
  # BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID","completion_code", 
           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28)%>%
  # drop anything with quantised or text
  select(-contains("text"))%>%
  select(-contains("quantised")))

bpq_names


# use the quantised columns as the response siunce they have a number rather than a string

db_BPQ1<- db_BPQ %>%
  
# score_BPQ <- function(df){
  # Create a new temporary df to store the BPQ data 
  # BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID","completion_code", 
           BAI_01:`BAI_26-quantised`, ANSR_01:`ANSR_20-quantised`, HHI_01:`HHI_28-quantised`)%>%
  # drop anything with quantised or text
  # library(dplyr) 
  select(-contains("text")) %>%
  # select(-contains("quantised"))%>%
  
  # select the quantised to use as the coded variable
  select(c(1:2, contains("quantised")))
  
# score
# assign new names replacing quantised column names with BPQ only item names
names(db_BPQ1)<- bpq_names

colnames(db_BPQ1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_BPQ2<- db_BPQ1%>%
    # Recode factors into numerics
    # mutate_at(vars(BAI_01:HHI_28), 
    #           funs(car::recode("Never" = 1, 
    #                          "Occasionally" = 2, 
    #                          "Sometimes" = 3, 
    #                          "Usually" = 4, 
    #                          "Always" = 5)))
  select(c(1:28))%>%
   mutate(BPQ = rowSums(.[ 3:28]))
    
  #   # Autonomic nervous system response
  #   ANSR_score = sumvars(.df = BPQ_data,
  #                        ANSR_01:ANSR_20) / 20,
  #   
  #   # Health history inventory
  #   HHI_score = sumvars(.df = BPQ_data,
  #                       HHI_01:HHI_28) / 28
  # )
  # 

db_BPQ2
db_BPQ3<- select(db_BPQ2, 1,2,29)
db_BPQ3
```

BVAQ: 83b1
https://www.psychologicabelgica.com/articles/10.5334/pb.302/print/
sum ramnge 40-200


hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

```{r}
# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1/356_357_611_616")

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_BVAQ_backup<- db_BVAQ

db_BVAQ_356<- subset(db_BVAQ, db_BVAQ$completion_code == "lvevkz")

db_BVAQ <- list.files(pattern = "*-83b1.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

library(readxl)
# db_BVAQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1/data_exp_11458-v9_questionnaire-83b1-4489770.xlsx")



# eliminate empty rows
db_BVAQ<- subset(db_BVAQ, db_BVAQ$`Event Index`== 1)

db_BVAQ$completion_code<- db_BVAQ$`Participant Completion Code`

View(db_BVAQ)

db_BVAQ<- bind_rows(db_BVAQ, db_BVAQ_356)

db_BVAQ1<- db_BVAQ %>%
   select( -contains("quantised"))%>%
   select(c("Participant Private ID","completion_code",BVAQ_01:BVAQ_40))

colnames(db_BVAQ1)

db_BVAQ1<- db_BVAQ1%>%
   mutate(BVAQ = rowSums(.[ 3:42]))
  
db_BVAQ3<- select(db_BVAQ1, c(1,2,43))

db_BVAQ3
```

demographics
8zto- age
8nsp - vision
v2gn = mental health

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn")

read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}


read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_age_backup<- db_age

db_age_356<- subset(db_age, db_age$`Participant Completion Code` == "lvevkz")

db_age <- list.files(pattern = "*-8zto.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_age<- bind_rows(db_age, db_age_356)


# db_age <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8zto-4489770.xlsx")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/vision8nsp")

db_vision_backup<- db_vision
db_vision_356<- subset(db_vision, db_vision$`Participant Completion Code` == "lvevkz")

db_vision <- list.files(pattern = "*-8nsp.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_vision<- bind_rows(db_vision, db_vision_356)


# db_vision <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8nsp-4489770.xlsx")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/vision8nsp")
db_mhealth_backup<- db_mhealth

db_mhealth_356<- subset(db_mhealth,db_mhealth$`Participant Completion Code` == "lvevkz")

db_mhealth <- list.files(pattern = "*-v2gn.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_mhealth$`mental_health-text`<- as.character(db_mhealth$`mental_health-text`)
db_mhealth<- bind_rows(db_mhealth, db_mhealth_356)


library(readxl)
# db_mhealth <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-v2gn-4489770.xlsx")

colnames(db_mhealth)
# db_mhealth<- subset(db_mhealth, -2:12,14:15,17:26)

# bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,35,36))
db_age1<- subset(db_age1, db_age1$`Event Index` == 1)
db_vision1<- subset(db_vision, db_vision$`Event Index` == 1)
db_mhealth1<- subset(db_mhealth, db_mhealth$`Event Index` == 1)


colnames(db_mhealth)

db_mhealth$ASD
db_mhealth$`ASD-text`
db_mhealth$clinical_diagnosis
db_mhealth$mental_health
db_mhealth$`mental_health-text`
db_mhealth$medication
db_mhealth1<- select(db_mhealth, c(1,13,16, 33,34,37:38,40))

colnames(db_mhealth1)

colnames(db_vision)
db_vision$EyesightResponse
db_vision1<- select(db_vision, c(1,13,16, 33,34,36:37))

colnames(db_vision1)


# db_age1<- select(db_age, c(1,13,16,35,36))
db_age1<- subset(db_age1, db_age1$`Event Index` == 1)
db_vision1<- subset(db_vision1, db_vision1$`Event Index` == 1)
db_mhealth1<- subset(db_mhealth1, db_mhealth1$`Event Index` == 1)

# note this is ignoring the last
db_demog <- left_join(db_vision1, db_mhealth1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))
  
db_demog <- left_join(db_demog,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))

db_demog$completion_code <- db_demog$`Participant Completion Code`

```


IQ
IQ: esh8

345 to 356 need to be scores separatelly

Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937

hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r}
# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8/356_357_611_616")


read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

library(readxl)
# db_IQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8/data_exp_60620-v2_task-esh8.xlsx")

db_IQ_backup<- db_IQ

db_IQ_356<- subset(db_IQ, db_IQ$`Participant Completion Code` =="lvevkz" )
colnames(db_IQ1)
db_IQ <- list.files(pattern = "*-esh8.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_IQ)
iqnames<- colnames(db_IQ1)
# db_IQ1<- select(db_IQ, c(1,12,15, 35,38:44))
db_IQ1<- select(db_IQ, iqnames)

db_IQ2<- subset(db_IQ1, !is.na(Response))
View(db_IQ2)

db_IQ3 <- db_IQ2%>%
  group_by(`Participant Private ID`, `Participant Completion Code`)%>%
  summarise_if(is.numeric, sum, na.rm = TRUE)


db_IQ3$Matrix_Total<- db_IQ3$Correct
db_IQ3$completion_code<- db_IQ3$`Participant Completion Code`

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,7,6))
  
```

Merge all into one self report

```{r}


db_demog$completion_code <- db_demog$`Participant Completion Code`
db_demog$`Participant Completion Code`<- NULL

# left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")

db_DASS4$`Participant Public ID`<-NULL

db_demog$`Event Index.x`<-NULL
db_DASS4$`Participant Private ID`<- NULL
db_AQ4$`Participant Private ID`<- NULL

db_BVAQ3$`Participant Private ID`<- NULL
db_IQ4$`Participant Private ID`<- NULL
db_BPQ3$`Participant Private ID`<- NULL


db_BPQ3
# 
# left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")

db_self_rep_backup<- db_self_rep

db_AQ4
# db_demog has priovate and code
db_code_private<- select(db_demog, c(completion_code, `Participant Private ID`))
db_IAS<- left_join(db_IAS,db_code_private, by = "completion_code")

# merge all side by side based on a comoon column
db_self_rep_temp<- left_join(db_demog, db_DASS4, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_TAS4, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_AQ4, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_BVAQ3, by = "completion_code")

db_self_rep_temp<- left_join(db_self_rep_temp, db_IQ4, by = "completion_code")

db_self_rep_temp<- left_join(db_self_rep_temp, db_BPQ3, by = "completion_code")
db_self_rep_temp<- left_join(db_self_rep_temp, db_IAS, by = "completion_code")


# db_self_rep <- Reduce(merge, list(db_demog$completion_code,db_DASS4,db_TAS4$completion_code, db_AQ4$completion_code, db_BVAQ3$completion_code, db_IQ4$completion_code, db_BPQ3,db_IAS$`Participant Private ID`))

db_demog
# db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)
db_self_rep_backup<- db_self_rep
db_self_rep<- db_self_rep_temp

db_self_rep
# write_csv(db_self_rep, "db_self_rep_345_356.csv")

# write_csv(db_self_rep, "db_self_rep_350.csv")

write_csv(db_self_rep, "db_self_rep_356_367_611_616.csv")

# db_IAS$
```



hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
```{r}
# STAI_T:: 5nzr

# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr/356_356_611_616")

# STAIS: 8rfo

read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}


library(readxl)
db_STAI_T <- read_excel("data_exp_11458-v9_questionnaire-5nzr_345_356.xlsx")

db_STAI_T_backup<- db_STAI_T

db_STAI_T_356<- subset(db_STAI_T, db_STAI_T$completion_code == "lvevkz")


db_STAI_T<- list.files(pattern = "*-5nzr.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_STAI_T_356$`Event Index`<- as.character(db_STAI_T_356$`Event Index`)

db_STAI_T<- bind_rows(db_STAI_T, db_STAI_T_356)

# eliminate empty rows
db_STAI_T<- subset(db_STAI_T, db_STAI_T$`Event Index`== 1)

db_STAI_T$completion_code<- db_STAI_T$`Participant Completion Code`


# use the quantised columns as the response siunce they have a number rather than a string

colnames(db_STAI_T)
db_STAI_T1<- db_STAI_T %>%
    select("Participant Private ID","completion_code", 
           STAI_01:STAI_20)%>%
  # drop anything with quantised or text
  select(-contains("quantised"))
  

  
# score


colnames(db_STAI_T1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_STAI_T2<- db_STAI_T1%>%
   mutate(STAIT = rowSums(.[ 3:22]))
    
colnames(db_STAI_T2)
db_STAI_T3<- select(db_STAI_T2, c(1:2, 23))
db_STAI_T3


library(readxl)
# db_STAI_S <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/data_exp_11458-v9_questionnaire-8rfo_345_356.xlsx")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/356_357_611_616")

db_STAI_S_backup<- db_STAI_S

db_STAI_S_546<- subset(db_STAI_S, db_STAI_S$completion_code == "lvevkz")



db_STAI_S<- list.files(pattern = "*-8rfo.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))


db_STAI_S_546$`Event Index`<- as.character(db_STAI_S_546$`Event Index`)

db_STAI_S<- bind_rows(db_STAI_S, db_STAI_S_546)

# eliminate empty rows
db_STAI_S <- subset(db_STAI_S, db_STAI_S$`Event Index`== 1)

db_STAI_S$completion_code<- db_STAI_S$`Participant Completion Code`


# use the quantised columns as the response siunce they have a number rather than a string

colnames(db_STAI_S)

db_STAI_S1<- db_STAI_S %>%
    select("Participant Private ID","completion_code", 
           STAIS_01:STAIS_20)%>%
  # drop anything with quantised or text
  select(-contains("quantised"))
  

  
# score


colnames(db_STAI_S1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_STAI_S2<- db_STAI_S1%>%
   mutate(STAIS = rowSums(.[ 3:22]))
    
colnames(db_STAI_S2)

db_STAI_S3<- select(db_STAI_S2, c(1:2, 23))
colnames(db_STAI_S3)

db_STAI<- left_join(db_STAI_S3, db_STAI_T3)

```


merge 
```{r}
db_self_rep
library(readr)
# db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
# View(db_self_rep_350_1)


db_self_rep$`Event Index.x`<- NULL
db_self_rep$`Event Index.y`<-NULL
db_self_rep_350_1$`Event Index.y`<- NULL

# db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
colnames(db_self_rep)

db_self_rep_345_356<- db_self_rep[,c(1:25)]

# library(readxl)
Interoception_Study_Logbook <- read_excel("Interoception Study Logbook.xlsx")

library(readxl)
Interoception_Study_Logbook <- read_excel("Interoception Study Logbook _with456_357_611_616.xlsx")
# View(Interoception_Study_Logbook_with456_357_611_616)
View(Interoception_Study_Logbook)


db_self_rep_345_356$completion_code

Interoception_Study_Logbook$completion_code

ssid<- select(Interoception_Study_Logbook, c(1:3))
ssid$completion_code<- ssid$`Completion Code`

db_self_rep_345_356<- left_join(db_self_rep_345_356,ssid, by = "completion_code")
# write_csv(db_self_rep_345_356, "db_self_rep_345_356_final.csv")
write_csv(db_self_rep_345_356, "db_self_rep_356_357_611_616_final.csv")
```

# - CHECK WASI M on the norms


db_age2<- subset(db_age1, !is.na(`Participant Private ID`))
db_age2

db_self_rep_345_356<- left_join(db_self_rep_345_356,db_age2)

db_self_rep_345_356

colnames(db_self_rep_345_356)

db_self_rep_345_356

db_self_rep_345_356<- left_join(db_self_rep_345_356, db_STAI)


```
