---
title: "Scoring_questionnaires2021"
author: "Helio"
date: "21/08/2021"
output: html_document
---

gorilla codes


STAI:: 5nzr
AQ:7uqw
STAIS: 8rfo
Demog: 8zto
BVAQ: 83b1
BPQ: bbc4
DASS: chif
IQ: esh8
IAS: jvi8
TAS:pdlt
demog_meantal health: v2gn

AQ_50

quick check that Lucys scoring are correct

```{r}
# Traditional scoring

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/data_exp_11458-v9 (2)/Select")

library(readr)

db_quest_checkAQ<- read_csv("data_exp_11458-v8_questionnaire-7uqw.csv")
View(db_quest_checkAQ)

library(tidyverse)
colnames(db_quest_checkAQ)

db_quest_checkAQ<- db_quest_checkAQ%>%
  select(c(16,31:130))
  
db_quest_checkAQ_1<- db_quest_checkAQ%>%
select(seq(1, 101, 2))



# create a prefix for AQ items
# https://it.unt.edu/sites/default/files/paste_jds_jun2013.pdf - some nice tips here
prefix<- "AQ_"

AQ_counter<- seq(1,50)


aq_labels<-paste(prefix, AQ_counter, sep = "")
# generate odd numbers to match the columns we wnt to keep
names<- c("completion_code", aq_labels)

# rename dataset
names(db_quest_checkAQ_1)<- names

db_quest_checkAQ_2<- db_quest_checkAQ_1 %>%
#   mutate_at(c('TAS_4', 'TAS_5', 'TAS_10', 'TAS_18', 'TAS_19'), 
#             funs(recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
# #    2, 4, 5, 6, 7, 9, 12, 13, 16, 18,
# # 19, 20, 21, 22, 23, 26, 33, 35, 39, 41, 42, 43, 45, 46
  mutate_at(c("AQ_2", "AQ_4", "AQ_5", "AQ_6", "AQ_7", "AQ_9", "AQ_12", "AQ_13", "AQ_16", "AQ_18",
                 "AQ_19","AQ_20", "AQ_21", "AQ_22", "AQ_23", "AQ_26", "AQ_33", "AQ_35", "AQ_39", "AQ_41",
                 "AQ_42",
                 "AQ_43", "AQ_45", "AQ_46"), 
            funs(ifelse(. <= 2, 1, 0)))%>%
            # funs(recode(., "1=1; 2=1; 3=0; 4=0")))%>%
   mutate_at(c("AQ_1", "AQ_3", "AQ_8", "AQ_10", "AQ_11", "AQ_14", "AQ_15", "AQ_17", "AQ_24", "AQ_25",
                 "AQ_27","AQ_28", "AQ_29", "AQ_30", "AQ_31", "AQ_32", "AQ_34", "AQ_36", "AQ_37", "AQ_38",
                 "AQ_40",
                 "AQ_44", "AQ_47", "AQ_48", "AQ_49", "AQ_50"), 
             funs(ifelse(. > 2, 1, 0)))
             # funs(recode(., "1=0; 2=0; 3=1; 4=1")))



db_quest_checkAQ_2%>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ_Total = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ_Total))
  ggplot(aes(TAS_Total, AQ_Total))+
  geom_point()+
  facet_grid(~Dataset)
  
```

this confirms that Lucy scoring is correct
also checked a few examples of TAS seem correct. but should note one inconsistency in the first participant (300)

AQ_50

```{r}

# 345_356
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_AQ <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_AQ<- subset(db_AQ, db_AQ$`Event Index`== 1)
  
  
View(db_AQ)

library(tidyverse)
colnames(db_AQ)

db_AQ1<- db_AQ%>%
  select(c(16,33:132))
  

colnames(db_AQ1)

db_AQ2<- db_AQ1%>%
select(seq(1, 101, 2))

# create a prefix for AQ items
# https://it.unt.edu/sites/default/files/paste_jds_jun2013.pdf - some nice tips here
prefix<- "AQ_"

AQ_counter<- seq(1,50)

aq_labels<-paste(prefix, AQ_counter, sep = "")
# generate odd numbers to match the columns we wnt to keep
names<- c("completion_code", aq_labels)

# rename dataset
names(db_AQ2)<- names

db_AQ3<- db_AQ2 %>%
#   mutate_at(c('TAS_4', 'TAS_5', 'TAS_10', 'TAS_18', 'TAS_19'), 
#             funs(recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
# #    2, 4, 5, 6, 7, 9, 12, 13, 16, 18,
# # 19, 20, 21, 22, 23, 26, 33, 35, 39, 41, 42, 43, 45, 46
  mutate_at(c("AQ_2", "AQ_4", "AQ_5", "AQ_6", "AQ_7", "AQ_9", "AQ_12", "AQ_13", "AQ_16", "AQ_18",
                 "AQ_19","AQ_20", "AQ_21", "AQ_22", "AQ_23", "AQ_26", "AQ_33", "AQ_35", "AQ_39", "AQ_41",
                 "AQ_42",
                 "AQ_43", "AQ_45", "AQ_46"), 
            funs(ifelse(. <= 2, 1, 0)))%>%
            # funs(recode(., "1=1; 2=1; 3=0; 4=0")))%>%
   mutate_at(c("AQ_1", "AQ_3", "AQ_8", "AQ_10", "AQ_11", "AQ_14", "AQ_15", "AQ_17", "AQ_24", "AQ_25",
                 "AQ_27","AQ_28", "AQ_29", "AQ_30", "AQ_31", "AQ_32", "AQ_34", "AQ_36", "AQ_37", "AQ_38",
                 "AQ_40",
                 "AQ_44", "AQ_47", "AQ_48", "AQ_49", "AQ_50"), 
             funs(ifelse(. > 2, 1, 0)))
             # funs(recode(., "1=0; 2=0; 3=1; 4=1")))



db_AQ4<- db_AQ3%>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ))
  



```

TAS-28

```{r}

read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

db_TAS <- list.files(pattern = "*-pdlt.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_TAS<- subset(db_TAS, db_TAS$`Event Index`== 1)
  
  
View(db_TAS)

library(tidyverse)
colnames(db_TAS)

db_TAS1<- db_TAS%>%
  select(c(16,33:71))
  

colnames(db_TAS1)

db_TAS2<- db_TAS1%>%
select(c(1,seq(2, 40, 2)))


db_TAS2
# note the gorilal tas labels have a zero, like 01 instead of 1
?recode
db_TAS3<- db_TAS2 %>%
  mutate_at(c('TAS_04', 'TAS_05', 'TAS_10', 'TAS_18', 'TAS_19'), 
            funs(car::recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
  mutate(DIF = TAS_01 + TAS_03 + TAS_06 + TAS_07 + TAS_09 + TAS_13+ TAS_14)%>%
  mutate(EOT = TAS_08+TAS_15+TAS_16+TAS_20+TAS_05+TAS_10+TAS_18+TAS_19)%>%
  mutate(DDF = TAS_02+TAS_11+TAS_12+TAS_17+TAS_04)%>%
  mutate(TAS = DIF + DDF + EOT)

db_TAS3$completion_code<- db_TAS3$`Participant Completion Code`

db_TAS4<- select(db_TAS3, c(completion_code, TAS))
  


```

DASS: chif

# Function that scores DASS-21 and all subscales. DASS-21 is a 21-item scale
# (0-3 likert) measuring the participant's levels of depression, anxiety, and 
# stress. DASS is based on a dimensional understanding of these factors - 
# each of the 21 items is mapped to one of the three factors.
# Dependencies: tidyverse, 03_scoring_helpers.R

subscales need to be multiplied by 2

```{r}
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_DASS <- list.files(pattern = "*-chif.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_DASS<- subset(db_DASS, db_DASS$`Event Index`== 1)

colnames(db_DASS)
db_DASS1<- db_DASS%>%
  select(c(12,13,16,33:73))
  
colnames(db_DASS1)


db_DASS2<- db_DASS1%>%
select(c(1:3,seq(4, 44, 2)))

db_DASS2$DASS_08<- db_DASS2$STAI_08
  
db_DASS2$STAI_08<- NULL

db_DASS3 <- db_DASS2 %>%
  # mutate(DASS_score_total =         rowsum(
  #                                      DASS_01:DASS_21))
  #   
    # Depression subscale is items 3, 5, 10, 13, 16, 17, and 21
    mutate(DASSDepression = 2*(DASS_03+ DASS_05+ DASS_10+ DASS_13+
                                       DASS_16+ DASS_17+ DASS_21),
    # Anxiety subscale is items 2, 4, 7, 9, 15, 19, and 20
    DASSAnxiety =    2*(DASS_02+ DASS_04+ DASS_07+ DASS_09+
                                       DASS_15+ DASS_19+ DASS_20),
    
    # Stress subsccale is items 1, 6, 8, 11, 12, 14, and 18
    # on gorilla DAS_08 is islabeled STAI_08
    DASSStress =     2*(DASS_01+ DASS_06+ DASS_08+ DASS_11+
                                       DASS_12+ DASS_14+ DASS_18)
    )%>%
  mutate(DASSTotal = DASSDepression+DASSAnxiety+DASSStress)
  
colnames(db_DASS3)
db_DASS3$completion_code<- db_DASS3$`Participant Completion Code`

db_DASS4<- select(db_DASS3, c(1:2,29,25:28))

```

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/
```{r eval=FALSE, include=FALSE}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)



```



BPQ: bbc4

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}
library(readxl)
db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
View(data_exp_11458_v9_questionnaire_bbc4)

db_BPQ <- list.files(pattern = "*-bbc4.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

# eliminate empty rows
db_BPQ<- subset(db_BPQ, db_BPQ$`Event Index`== 1)

db_BPQ$completion_code<- db_BPQ$`Participant Completion Code`

# store names for BPQ columns
bpq_names<- names(db_BPQ %>%
  
# score_BPQ <- function(df){
  # Create a new temporary df to store the BPQ data 
  # BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID","completion_code", 
           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28)%>%
  # drop anything with quantised or text
  select(-contains("text"))%>%
  select(-contains("quantised")))

bpq_names


# use the quantised columns as the response siunce they have a number rather than a string

db_BPQ1<- db_BPQ %>%
  
# score_BPQ <- function(df){
  # Create a new temporary df to store the BPQ data 
  # BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID","completion_code", 
           BAI_01:`BAI_26-quantised`, ANSR_01:`ANSR_20-quantised`, HHI_01:`HHI_28-quantised`)%>%
  # drop anything with quantised or text
  # library(dplyr) 
  select(-contains("text")) %>%
  # select(-contains("quantised"))%>%
  
  # select the quantised to use as the coded variable
  select(c(1:2, contains("quantised")))
  
# score
# assign new names replacing quantised column names with BPQ only item names
names(db_BPQ1)<- bpq_names

colnames(db_BPQ1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_BPQ2<- db_BPQ1%>%
    # Recode factors into numerics
    # mutate_at(vars(BAI_01:HHI_28), 
    #           funs(car::recode("Never" = 1, 
    #                          "Occasionally" = 2, 
    #                          "Sometimes" = 3, 
    #                          "Usually" = 4, 
    #                          "Always" = 5)))
  select(c(1:28))%>%
   mutate(BPQ = rowSums(.[ 3:28]))
    
  #   # Autonomic nervous system response
  #   ANSR_score = sumvars(.df = BPQ_data,
  #                        ANSR_01:ANSR_20) / 20,
  #   
  #   # Health history inventory
  #   HHI_score = sumvars(.df = BPQ_data,
  #                       HHI_01:HHI_28) / 28
  # )
  # 

db_BPQ2
db_BPQ3<- select(db_BPQ2, 1,2,29)
```

BVAQ: 83b1
https://www.psychologicabelgica.com/articles/10.5334/pb.302/print/
sum ramnge 40-200

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

db_BVAQ <- list.files(pattern = "*-83b1.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))


# eliminate empty rows
db_BVAQ<- subset(db_BVAQ, db_BVAQ$`Event Index`== 1)

db_BVAQ$completion_code<- db_BVAQ$`Participant Completion Code`

View(db_BVAQ)

db_BVAQ1<- db_BVAQ %>%
   select( -contains("quantised"))%>%
   select(c("Participant Private ID","completion_code",BVAQ_01:BVAQ_40))

db_BVAQ1<- db_BVAQ1%>%
   mutate(BVAQ = rowSums(.[ 3:42]))
  
db_BVAQ3<- select(db_BVAQ1, c(1,2,43))
```

demographics
8zto- age
8nsp - vision
v2gn = mental health

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn")

read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

db_age <- list.files(pattern = "*-8zto.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_vision <- list.files(pattern = "*-8nsp.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))
db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_mhealth)
# db_mhealth<- subset(db_mhealth, -2:12,14:15,17:26)

bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,36,37,41))

colnames(db_mhealth)

db_mhealth$ASD
db_mhealth$`ASD-text`
db_mhealth$clinical_diagnosis
db_mhealth$mental_health
db_mhealth$`mental_health-text`
db_mhealth$medication
db_mhealth1<- select(db_mhealth, c(1,13,16, 33,34,37:38,40))

colnames(db_vision)
db_vision$EyesightResponse
db_vision1<- select(db_vision, c(1,13,16, 33,34,36:37))

db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))%>%
  subset(!is.na(`Participant Private ID`))

db_demog$completion_code <- db_demog$`Participant Completion Code`

```


IQ
IQ: esh8

345 to 356 need to be scores separatelly

Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")


read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

db_IQ <- list.files(pattern = "*-esh8.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_IQ)

db_IQ1<- select(db_IQ, c(1,13,16, 37,45:48))

db_IQ2<- subset(db_IQ1, !is.na(Response))
View(db_IQ2)

db_IQ3 <- db_IQ2%>%
  group_by(`Participant Private ID`, `Participant Completion Code`)%>%
  summarise_if(is.numeric, sum, na.rm = TRUE)


db_IQ3$Matrix_Total<- db_IQ3$Correct
db_IQ3$completion_code<- db_IQ3$`Participant Completion Code`

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,7,6))
  
```

Merge all into one self report

```{r}
db_demog$`Participant Completion Code`<- NULL

db_demog$completion_code<- db_demog$`Participant Completion Code`

left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")

db_DASS4$`Participant Public ID`<-NULL

db_demog$`Event Index.x`<-NULL
db_DASS4$`Participant Private ID`<- NULL
db_AQ4$`Participant Private ID`<- NULL

db_BVAQ3$`Participant Private ID`<- NULL
db_IQ4$`Participant Private ID`<- NULL
db_BPQ3$`Participant Private ID`<- NULL


db_BPQ3

left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")


db_self_rep<- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))

# db_IAS$
```